Detecting threats of violence in YouTube comments

### 2016-02-17 submission.tex
Added experimental setup

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2016}
\usepackage{times}
\usepackage{latexsym}

@@

\usepackage{pgfplots}
% Anbefalt her: https://www.sharelatex.com/learn/Pgfplots_package#Introduction
\pgfplotsset{width=10cm}

@@

@@

In this article, we evaluate different types of features for the task
of detecting threats of violence in YouTube comments. We show that ...

@@

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. The topics included sexuality, race,
culture and intelligence. The comments were grouped by topic, and then
12~\% of these were manually annotated to check that they were placed
in the right category.
The first stage of the detection was the same across all
categories. It consisted of using a lexicon of negative words and a
list of profane words, as well as part-of-speech tags from the
training data that were correlated with bullying. The second stage was
category-specific, and used commonly observed uni- and bigrams from
each category as features. The experiments reported accuracies from
63~\% to 80~\%, but did not report precision or recall.

There has been quite a bit of work focused on the detection of threats
in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
The data set used for these experiments consisted a collection of 5000
threatening tweets collected by a website over a period of about two
years. In addition, a large number of random tweets were collected for
development and testing. A set of 2.3 million random tweets was used
for development, and a set of 1 million was used for testing. This set
was not annotated in any way prior to being used in the experiments.
The system relies on manually constructed recognition patterns, in the
form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
trigrams), but do not go into detail about the methods used to
construct these patterns, stating that the researchers relied on their
(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
\newcite{nellshallow2013}, a manually crafted shallow parser is added
to the system. This improves results to a precision of 39\% and a
recall of 59\%.

\newcite{warner2012} present a method for detecting unwanted or
illegal comments in user-generated web text from the internet, which
relies on machine learning in combination with template-based
features. The data set used in the research came from two sources. The
first consists of posts from Yahoo news groups, the second were
webpages collected by the American Jewish Congress that had been
identified as offensive. The data set was manually annotated, and then
the hate speech was assigned to a category, such as antisemitic,
anti-woman, anti-asian, etc. The research then focused on the
antisemitic category.  The research approaches the problem as a
word-sense disambiguation task, since the same words can be used in
both hateful and non-hateful contexts. The features used in the
classification were combinations of uni-, bi- and trigrams,
part-of-speech-tags and Brown clusters.  The best results of the
classifications were obtained using only unigrams as features, with a
precision of 67~\% and a recall of 60~\%. The other feature sets
garnered much lower results, and the authors suggest that deeper
parsing could reveal significant phrase patterns.

@@

\section{Experiments}
\label{sec:exp}

\subsection{Experimental setup}
The data set is split into an 80-20 training and testing set. All
tuning and development experiments were performed using 10-fold
cross-validation on the training set.

Since threat annotation is performed on the sentence level, the data
set has been manually split into sentences as part of the annotation
process.  We performed tokenization, lemmatization, PoS-tagging and
dependency parsing using the spaCy toolkit REF.  SpaCy assigns both
the standard Penn Treebank PoS-tags REF, as well as the more
coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
dependency parser assigns an analysis in compliance with the ClearNLP
converter REF. The data set was further enriched with the cluster
labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created
using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced
from the RCV1 corpus, a corpus containing Reuters English newswire
text, with approximately 63 million words and 3.3 million sentences.
WordNet REF

%% todo:
%% - data split
%% - preprocessing
%%   Spacy, Brown clusters, WordNet
%% - machine learner
%% - tuning
%% - feature templates

\subsection{Results}

@@

\subsection{Held-out results}

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage{naaclhlt2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{relsize}

@@

\usepackage{tikz-qtree}
\usepackage{tikz-dependency}

@@

\let\tag=\textsc

@@

In this article, we evaluate different types of features for the task
of detecting threats of violence in YouTube comments. We draw on both
lexical, morphosyntactic and lexical semantic information sources and
experiment with different machine learning algorithms. Our results
indicate that successful detection of threats of violence is largely
determined by lexical information.

@@

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. They adopt a two-stage approach, where the
first stage consists of using a lexicon of negative words and a list
of profane words, as well as part-of-speech tags from the training
data that were correlated with bullying. The second stage is
category-specific, and makes use of commonly observed uni- and bigrams
from each category as features. The experiments reported accuracies
from 63~\% to 80~\%, but did not report precision or recall.
% lists of negative and profane words
% correlated words from training data

There has been quite a bit of work focused on the detection of threats
in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
The data set used for these experiments consists of a collection of 5000
threatening tweets collected by a website over a period of about two
years. In addition, a large number of random tweets were collected for
development and testing. A set of 2.3 million random tweets was used
for development, and a set of 1 million was used for testing. 
The system relies on manually constructed recognition patterns, in the
form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
trigrams), but do not go into detail about the methods used to
construct these patterns, stating that the researchers relied on their
(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
\newcite{nellshallow2013}, a manually crafted shallow parser is added
to the system. This improves results to a precision of 39\% and a
recall of 59\% \footnote{Perhaps a footnote on the peculiarities of the evaluation??}.
% handcrafted patterns
% rule-based shallow parser
% dubious evaluation

\newcite{warner2012} present a method for detecting unwanted or
illegal comments in user-generated web text from the internet, which
relies on machine learning in combination with template-based
features. The data set used in the research came from two sources. The
first consists of posts from Yahoo news groups, the second were
webpages collected by the American Jewish Congress that had been
identified as offensive. The data set was manually annotated, and then
the hate speech was assigned to a category, such as anti-Semitic,
anti-woman, anti-Asian, etc. The task is then approached as a
word-sense disambiguation task, since the same words can be used in
both hateful and non-hateful contexts. The features used in the
classification were combinations of uni-, bi- and trigrams,
part-of-speech-tags and Brown clusters.  The best results of the
classifications were obtained using only unigrams as features, with a
precision of 67~\% and a recall of 60~\%. The other feature sets
garnered much lower results, and the authors suggest that deeper
parsing could reveal significant phrase patterns.
% only unigrams best results
% suggests parsing might help

\newcite{hammer2014} reports an experiment on the data set that we
will be using in our own experiments, although it has been changed
slightly since the publication of his initial study. The method used a
logistic LASSO regression analysis on bigrams (skip-grams) of
important words to classify sentences as \tovs{} or not.
The method described in the article uses a set of important words that
are correlated with threats of violence. The features are bigrams of
two of these important words observed in the same sentence. The
article does not describe exactly how these important words were
selected, stating only that words were chosen that were significantly
correlated with the response (violent/non-violent sentence). Results are reported only in terms of proportion of false positives for the two classes and it is not clear how the data was split for training and evaluation.

@@

\section{Experiments}
\label{sec:exp}
Much of the previous work in Section \ref{sec:prev} made use of
precompiled lists of correlated words and manually crafted
patterns. Whereas these resources can be effective, they are highly
task-specific and do not easily lend themselves to replication.  The
previous work further highlights the effectiveness of lexical features
(words-based features), however, several of the authors suggest that parsing
may be beneficial for these tasks.

In this work we experiment with a wide range of linguistic information
as features in our system and investigate the introduction of
linguistic context through a set of feature templates. We also
generalize these features through a backoff technique. Throughout, we
make use of freely available, re-usable resources and tools in order
to construct our system.

\subsection{Experimental setup}

\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the data
set has been manually split into sentences as part of the annotation
process.  We performed tokenization, lemmatization, PoS-tagging and
dependency parsing using the SpaCy
toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard
Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more
coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
dependency parser assigns an analysis in compliance with the ClearNLP
converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example
dependency graph from the data set. The data set was further enriched
with the cluster labels described in Turian et
al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering
algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
corpus containing Reuters English newswire text, with approximately 63
million words and 3.3 million sentences. We vary the number of clusters to be either 100,
320, 1000 or 3200 clusters and use the full cluster label.
 WordNet REF

\begin{figure*}
\begin{dependency}[arc edge, text only label, theme=simple]
  \begin{deptext}[column sep=.2cm]
    i \& m \& fucking \& scared \& kill \& them \& d \& : \\
   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
  \end{deptext}
  \depedge{2}{1}{\large nsubj}
  \depedge{2}{8}{\large punct}
  \depedge{2}{4}{\large acomp}
  \depedge{4}{3}{\large amod}
  \depedge{2}{5}{\large conj}
  \depedge{5}{6}{\large dobj}
  \depedge{5}{7}{\large advmod}
  \deproot[edge unit distance=1.5ex]{2}{}
\end{dependency}
\caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
\label{fig:dep}
\end{figure*}

\paragraph{Classifiers}

\paragraph{Tuning}

\paragraph{Features}
Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
\begin{description}
\setlength\itemsep{0em}
\item[Lexical] word form, lemma
\item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
\item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
\end{description}
These features are structured according to a set of \emph{feature
  templates}, which introduce varying degrees of linear order and
syntactic context: bag-of-features (unordered), bigrams, trigrams and
dependency triples. These feature templates are applied to the feature
types presented above, in order to yield features like the following
for our examples sentence in Figure \ref{fig:dep}:

\begin{itemize}
\setlength\itemsep{0em}
\item \{i m,  m fucking, fucking scared, scared kill, kill them,  them d,  d :\}

\item \{PRON VERB VERB, VERB VERB ADJ, VERB ADJ VERB, ADJ VERB PRON,  VERB PRON X,  PRON X PUNCT\}

\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
\end{itemize}
Our lexical features are very specific and require the exact
combination of two lexical items in order to apply to a new instance.
Following \newcite{Jos:Pen:2009}, we therefore experiment with
generalization of features by backoff to a more general category,
e.g. from word form to lemma or PoS. A dependency triple over word
forms like $<$kill, dobj, them$>$ would thus be generalized to
$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
trigram and dependency triple features.
\subsection{Results}

@@

\subsection{Held-out results}M
